;-- Транспорт 
[vehicle]
GroupControlSection	= spawn_group
class			    = SCRPTCAR
cform               = skeleton
ef_equipment_type	= 3

;-- Нива.
[vehicle_niva]:vehicle
$spawn 			= "vehicles\vehicle_niva"
visual          = physics\vehicles\niva\veh_niva_u_01.ogf
actor_visual	= physics\vehicles\niva\veh_niva_u_01.ogf

;-- Еще Нива.
[vehicle_niva2]:vehicle
$spawn 			= "vehicles\vehicle_niva2"
visual          = physics\vehicles\niva\veh_niva_u_02.ogf
actor_visual	= physics\vehicles\niva\veh_niva_u_02.ogf

;-- Москвич.
[vehicle_moskvich]:vehicle
$spawn 			= "vehicles\vehicle_moskvich"
visual          = physics\vehicles\moskvich\veh_moskvitch_u_01.ogf
actor_visual	= physics\vehicles\moskvich\veh_moskvitch_u_01.ogf

;-- Зеленый
[vehicle_moskvich2]:vehicle
$spawn 			= "vehicles\vehicle_moskvich"
visual          = physics\vehicles\moskvich\veh_moskvitch_u_02.ogf
actor_visual	= physics\vehicles\moskvich\veh_moskvitch_u_02.ogf

;-- УАЗ. Новый
[vehicle_uaz]:vehicle
$spawn 			= "vehicles\vehicle_uaz"
visual          = physics\vehicles\uaz\veh_uaz_u_01.ogf
actor_visual	= physics\vehicles\uaz\veh_uaz_u_01.ogf

;-- УАЗ. Старый
[vehicle_uaz2]:vehicle
$spawn 			= "vehicles\vehicle_uaz"
visual          = physics\vehicles\uaz\veh_uaz_u_02.ogf
actor_visual	= physics\vehicles\uaz\veh_uaz_u_02.ogf

;-- Запорожец. Горбатый
[vehicle_zaz]:vehicle
$spawn 			= "vehicles\vehicle_zaz"
visual          = physics\vehicles\zaz\veh_zaz_u_01.ogf
actor_visual	= physics\vehicles\zaz\veh_zaz_u_01.ogf

;-- Запорожец. Ушастый
[vehicle_zaz968]:vehicle
$spawn 			= "vehicles\vehicle_zaz968"
visual          = physics\vehicles\zaz968\veh_zaz_968.ogf
actor_visual	= physics\vehicles\zaz968\veh_zaz_968.ogf

;-- ВАЗ 2106.
[vehicle_2106]:vehicle
$spawn 			= "vehicles\vehicle_2106"
visual          = physics\vehicles\vaz_2106\2106.ogf
actor_visual	= physics\vehicles\vaz_2106\2106.ogf

;-- УАЗ буханка.
[vehicle_uazbuhanka]:vehicle
$spawn 			= "vehicles\vehicle_uazbuhanka"
visual          = physics\vehicles\uaz_buhanka\uaz_buhanka.ogf
actor_visual	= physics\vehicles\uaz_buhanka\uaz_buhanka.ogf

;-- Автобус ЛАЗ.
[vehicle_avtobuslaz]:vehicle
$spawn 			= "vehicles\vehicle_avtobuslaz"
visual          = physics\vehicles\avtobus_laz\avtobus_laz.ogf
actor_visual	= physics\vehicles\avtobus_laz\avtobus_laz.ogf

;-- Автобус ГАЗ-53.
[vehicle_avtobuszil]:vehicle
$spawn 			= "vehicles\vehicle_avtobuszil"
visual          = physics\vehicles\avtobus_gaz\avtobus_gaz.ogf
actor_visual	= physics\vehicles\avtobus_gaz\avtobus_gaz.ogf

;-- Грузовик ЗИЛ ММЗ.
[vehicle_zil_mmz]:vehicle
$spawn 			= "vehicles\vehicle_zil_mmz"
visual          = physics\vehicles\zil_mmz\zil_mmz.ogf
actor_visual	= physics\vehicles\zil_mmz\zil_mmz.ogf

;-- Грузовик ЗИЛ 131.
[vehicle_zil131]:vehicle
$spawn 			= "vehicles\vehicle_zil131"
visual          = physics\vehicles\zil_131\zil_131.ogf
actor_visual	= physics\vehicles\zil_131\zil_131.ogf

;-- Камаз
[vehicle_kamaz]:vehicle
$spawn 			= "vehicles\vehicle_kamaz"
visual          = physics\vehicles\kamaz\veh_kamaz_u_01.ogf
actor_visual	= physics\vehicles\kamaz\veh_kamaz_u_01.ogf

;-- Камаз без прицепа.
[vehicle_kamaz_nopricep]:vehicle
$spawn 			= "vehicles\vehicle_kamaz_nopricep"
visual          = physics\vehicles\kamaz\veh_kamaz_nopricep_u_01.ogf
actor_visual	= physics\vehicles\kamaz\veh_kamaz_nopricep_u_01.ogf

;-- ГАЗ 66.
[vehicle_gaz66]:vehicle
$spawn 			= "vehicles\vehicle_gaz66"
visual          = physics\vehicles\gaz66\gaz66.ogf
actor_visual	= physics\vehicles\gaz66\gaz66.ogf

;-- Трактор.
[vehicle_tr13]:vehicle
$spawn 			= "vehicles\vehicle_tr13"
visual          = physics\vehicles\tr13\veh_tr13_u_01.ogf
actor_visual	= physics\vehicles\tr13\veh_tr13_u_01.ogf

;-- БТР.
[vehicle_btr]:vehicle
$spawn 			= "vehicles\vehicle_btr"
visual          = physics\vehicles\btr\veh_btr_u_09.ogf
actor_visual	= physics\vehicles\btr\veh_btr_u_09.ogf

[esc_vehicle_btr]:vehicle
$spawn          = "vehicles\esc_vehicle_btr"
visual          = physics\vehicles\btr\veh_btr_u_01.ogf
actor_visual    = physics\vehicles\btr\veh_btr_u_01.ogf
script_binding  = bind_physic_object.init
custom_data     = scripts\esc\esc_btr_unmove.ltx